%!TEX root = ../cv.tex

\cvsection{Research Projects}

\begin{cventries}
	\cventry
		{Guide: Prof. Ravi Banavar, Systems and Control Engineering, IIT Bombay}
		{Design of a discrete observer for a dynamical system on SO(3)}
		{Usually, systems are modelled as continuous time systems. However, the measurement of their states, using any kind of device, is performed in discrete time. The effect of this discretization is seen when the measurements are sparse. Hence, we intend to develop a discrete time observer for a continuous time system on the SO(3), with the system dynamics as the rotation dynamics.}
		{March 2018 - Present}
		{
		\begin{cvitems}
			\item Studied various existing continuous time observers and discrete time observers for the system on the manifold
			\item Studied various discretization techniques for dynamical systems evolving on manifolds
		\end{cvitems}
		}

	\cventry
		{Guide: Prof. Abhishek Gupta, Department of Mechanical Engineering, IIT Bombay}
		{Design of a capacitive sensor}
		{The intention of this project was to detect the number of capsules or tablets passing through a given point in the commercial line and measure the amount they were filled non-invasively and without disrupting the flow of the manufacturing system.}
		{December 2015 - December 2016}
		{
		\begin{cvitems}
			\item Used mechanical design tools like solidworks for designing sensor and implemented it for solid, liquid filled capsules, and tablets.
			\item Designed faraday cage for compactness, reducing noise by 90\% and implemented an aray for multiple lines of sensors.
		\end{cvitems}
		}

	\cventry
		{Guide: Prof. Ravi Banavar, Systems and Control Engineering, IIT Bombay}
		{Simulation and Control of Purcell Swimmer}
		{}
		{December 2016}
		{
		\begin{cvitems}
			\item Simulated a 2D purcell swimmer in Python following different gaits for pure translation along individual axes and pure rotation
		\end{cvitems}
		}
\end{cventries}